Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-03-03 Scripts/Initial_Analysis.Rmd
Included a catch proportion in proportion analysis

  #Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(taxon_key,
             eez_name,
             year,
             ensemble) %>% 
    summarise(n_spp_eez = length(unique(index))) %>% 
    left_join(Neighbours_List,
              by = "eez_name")

  # Split dataframes to merge latter
  Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      Name=eez_name,
      n_spp_eez,
      year,
      ensemble
    )

  Neighbour_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      n_spp_eez,
      Name=eez_neighbour,
      eez_name,
      year,
      ensemble
    )

  # Estimate Area index and % change
  Per_Ghange_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Name","taxon_key","year","ensemble")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(eez_name = Name,
           eez_neighbour =eez_name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(area_index = n_spp_Country/Spp_Total) %>% 
    # Determine the three time frames for comparrison
    mutate(
      time_step = ifelse(year < hist_y,"historical",
                         ifelse(year >= 2021 & year <= 2040, "early",
                                ifelse(year >= 2041 & year <= 2060, "mid","NA")
                         )
      )
    ) %>%
    filter(time_step != "NA") %>% 
    # Time mean and sd
    ungroup() %>% 
    group_by(taxon_key,ensemble,eez_name,eez_neighbour,time_step) %>% 
    summarise_at(vars("area_index"),
                 c(temporal_mean=mean,
                   temporal_sd=sd)
    ) %>% 
    # ensemble mean and sd
    group_by(taxon_key,eez_name,eez_neighbour,time_step) %>%
    summarise(
      ensemble_mean = mean(temporal_mean, na.rm = T),
      ensemble_sd = sd(temporal_mean, na.rm = T),
      ensemble_n = n()
    )

@@

# EstPropChange(taxon_key = 600004,
#               year = year_df$year,
#               hist_y = 2000,
#               data_type = "Catch",
#               ensemble_list = 102,
#               path = path,
#               neighbours = neighbours)
#

>>>>

  #Determines the amount of catch present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(taxon_key,
             eez_name,
             year,
             ensemble) %>% 
    summarise(n_spp_eez = length(unique(index)),
              total_mcp = sum(value)
              ) %>% 
    left_join(Neighbours_List,
              by = "eez_name")

  # Split dataframes to merge latter
  Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      Name=eez_name,
      n_spp_eez,
      total_mcp,
      year,
      ensemble
    )

  Neighbour_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      n_spp_eez,
      total_mcp,
      Name=eez_neighbour,
      eez_name,
      year,
      ensemble
    )

  # Estimate Area index and % change
  Per_Ghange_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Name","taxon_key","year","ensemble")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T),
           MCP_Total = sum(total_mcp.x,total_mcp.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(eez_name = Name,
           eez_neighbour =eez_name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y,
           mcp_Country = total_mcp.x,
           mcp_Neighbour = total_mcp.y) %>% 
    mutate(area_index = n_spp_Country/Spp_Total,
           catch_proportion = mcp_Country/MCP_Total) %>% 
    # Determine the three time frames for comparrison
    mutate(
      time_step = ifelse(year < hist_y,"historical",
                         ifelse(year >= 2021 & year <= 2040, "early",
                                ifelse(year >= 2041 & year <= 2060, "mid","NA")
                         )
      )
    ) %>%
    filter(time_step != "NA") %>% 
    # Time mean and sd
    ungroup() %>% 
    group_by(taxon_key,ensemble,eez_name,eez_neighbour,time_step) %>% 
    summarise_at(vars("area_index","catch_proportion"),
                 c(temp_mean=mean,
                   tempo_sd=sd)
    ) %>% 
    # ensemble mean and sd
    group_by(taxon_key,eez_name,eez_neighbour,time_step) %>%
    summarise_at(vars("area_index_temp_mean","catch_proportion_temp_mean"),
                 c(ensemble_mean = mean,
                   ensemble_sd = sd
                   )
    )

@@

EstPropChange(taxon_key = 600004,
              year = year_df$year,
              hist_y = 2000,
              data_type = "Catch",
              ensemble_list = c(102,103,104),
              # path = path,
              neighbours = neighbours)
